%% CV - Prof. Muaaz Bhamjee
%% Converted from MS Word document

\documentclass[11pt, a4paper]{article}

% ---- Packages ----
\usepackage[a4paper, top=2.0cm, bottom=2.0cm, left=2.2cm, right=2.2cm]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{array}
\usepackage{booktabs}
\usepackage{longtable}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}

% ---- Hyperlink styling ----
\hypersetup{
    colorlinks=true,
    linkcolor=blue!70!black,
    urlcolor=blue!70!black,
    citecolor=blue!70!black
}

% ---- Section formatting ----
\titleformat{\section}
  {\large\bfseries\uppercase}
  {}
  {0em}
  {}
  [\titlerule]

\titlespacing{\section}{0pt}{12pt}{6pt}

% ---- List settings ----
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=1.5em}

% ---- No paragraph indent ----
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

% ===============================================================
\begin{document}

% ---- Header ----
\begin{center}
  {\LARGE\bfseries Muaaz Bhamjee}\\[4pt]
  {\large Associate Professor, Department of Mechanical and Aeronautical Engineering}\\[2pt]
  {\large University of Pretoria}\\[6pt]
  Mobile: +27 76 476 4434 \quad Office: +27 12 420 5366 \quad
  Email: \href{mailto:muaaz.bhamjee@up.ac.za}{muaaz.bhamjee@up.ac.za}\\
  Language: English \quad Gender: Male \quad Citizenship: South African
\end{center}

% ===============================================================
\section{About Me}

Prof.\ Muaaz Bhamjee is currently an Associate Professor in the Department of Mechanical and Aeronautical Engineering at the University of Pretoria. He is the Founder and Principal Investigator of CERG-FLUX Lab -
Fluids, Learning, and Uncertainty in compleX systems. He has a background in Mechanical Engineering and Applied Mathematics. He is involved in research and has published in the fields of Computational Fluid Dynamics (CFD), Experimental High Energy Physics (HEP), Heat and Mass Transfer, Experimental Fluid Dynamics, Lattice Boltzmann Modelling, Multiphase Flow, Positron Emission Particle Tracking (PEPT), High Performance Computing (HPC), Solar and Renewable Energy, Solar Air Heating, Atomic Layer Deposition (ALD) Modelling, Fluid-Structure Interaction (FSI), Fluid Dynamics in Biomedical Applications and Engineering Education. The primary focus of his research was in the use of Navier-Stokes and Lattice-Boltzmann based computational fluid dynamics (CFD) approaches in modelling of the multi-scale fluid dynamics, heat and mass transfer processes and AI and data-driven approaches to Climate. Currently he is involved in research related to data driven and machine learning approaches to fluid dynamics, high energy physics, dynamical systems and hybrid quantum computing and machine learning approaches to such.

Prof.\ Bhamjee's prior experience includes roles as Staff Research Scientist at IBM Research -- Africa, Senior Research Associate (Visiting) at University of Johannesburg, Senior Lecturer (and prior Lecturer) at University of Johannesburg as well as Junior Computational Fluid Dynamics (CFD) Analyst at Hatch Africa.

% ===============================================================

\section{Research Lab Leadership}

Founder and Principal Investigator, CERG-FLUX Lab (2026–present)
Fluids, Learning, and Uncertainty in compleX systems
Research subgroup within the Clean Energy Research Group (CERG)
Department of Mechanical and Aeronautical Engineering, University of Pretoria

% ===============================================================

\section{Professional Profiles}

\begin{tabular}{@{}lll@{}}
\textbf{LinkedIn} & \multicolumn{2}{l}{\href{https://www.linkedin.com/in/muaaz-bhamjee-ding-mechanical-preng-000b7212/}{linkedin.com/in/muaaz-bhamjee-ding-mechanical-preng-000b7212}} \\[2pt]
\textbf{UP Profile} & \multicolumn{2}{l}{\href{https://www.up.ac.za/mechanical-and-aeronautical-engineering/view/staffprofile/43445}{up.ac.za -- Staff Profile}} \\[2pt]
\textbf{SAAM ExCo} & \multicolumn{2}{l}{\href{https://saam.africa/exco/}{saam.africa/exco}} \\
\end{tabular}

% ===============================================================
\section{Research Profiles}

\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Profile} & \textbf{ID} & \textbf{Link} & \textbf{H-index} \\
\midrule
Google Scholar & Dr.\ Muaaz Bhamjee & \href{https://scholar.google.co.za/citations?hl=en&user=jlOJkoAAAAJ&view_op=list_works&sortby=pubdate}{Link} & 62 \\
ORCID & 0000-0002-2697-4589 & \href{http://orcid.org/0000-0002-2697-4589}{Link} & N/A \\
Scopus & 55247084100 & \href{https://www.scopus.com/authid/detail.uri?authorId=55247084100}{Link} & 31 \\
ResearchGate & Muaaz Bhamjee & \href{https://www.researchgate.net/profile/Muaaz-Bhamjee}{Link} & 31 \\
Web of Science & ABE-4708-2020 & \href{https://www.webofscience.com/wos/author/record/ABE-4708-2020}{Link} & 27 \\
\bottomrule
\end{tabular}

% ===============================================================
\section{Fields of Specialisation}

\begin{itemize}
  
  \item Computational Fluid Dynamics (CFD).
  \item Mechanics (Statics and Dynamics).
  \item Heat and mass transfer.
  \item Multiphase flow.
  \item Navier-Stokes and Lattice Boltzmann based computational methods for modelling fluid flow, heat and mass transfer.
  \item Numerical analysis.
  \item Data Science, Machine Learning, Deep Learning.
  \item Geospatial Data Analysis and Climate Sciences.
  \item High Performance Computing (HPC) -- application of HPC to modelling.
  \item Solar and Renewable Energy / Solar Air Heating.
  \item Positron Emission Particle Tracking (PEPT): application and source preparation.
  \item Course co-ordination and lecturing.
  \item Scholarship of teaching and learning: Engineering education research with a focus on design literacy, online and blended learning.
\end{itemize}

% ===============================================================
\section{Professional Skills}

\begin{itemize}
  \item Research and Patent Ideation.
  \item Significant experience in research environments in academia and in industry.
  \item Journal and conference paper reviewing.
  \item Post-graduate supervision.
  \item Mentoring of Interns and Students.
  \item Project Management and Leadership.
  \item Course co-ordination and lecturing; Programme co-ordination.
  \item Supervision of final year students for their capstone research and design projects.
  \item Familiar with the engineering consulting and process engineering environments.
  \item Technical report writing; Teaching academic writing.
  \item Interpersonal skills; Teamwork and co-ordination; Mentoring.
\end{itemize}

% ===============================================================
\section{Technical Skills}

\begin{itemize}
  \item Proficient in Python for data science, machine and deep learning and solving of mathematical problems and general programming.
  \item Experience with Python-based Machine and Deep Learning Frameworks: PyTorch, TensorFlow and Keras, as well as scikit-learn.
  \item Geospatial and Climate Data Analysis.
  \item Computer Science and Software Engineering Skills: DevOps, Agile Development and Scrum, Cloud Computing, Unix/Linux and Shell Scripting, Git and GitHub, Containerisation of applications/software, Kubernetes and OpenShift.
  \item Proficient with ANSYS Fluent for CFD.
  \item Proficient with Palabos -- open-source libraries for Lattice Boltzmann based approach to CFD.
  \item Proficient in HPC hardware selection and application of HPC.
  \item Proficient with Matlab, Simulink, Maxima, GNU Plot, Excel and C++ for solving of mathematical problems and general programming.
  \item Proficient in \LaTeX{} for general and mathematical typesetting.
  \item Proficient with Microsoft Office and OpenOffice.
\end{itemize}

% ===============================================================
\section{Tertiary Education}

\textbf{Doctor of Engineering (DIng Mechanical Engineering Science)}\\
\textit{University of Johannesburg} \hfill 2011--2017\\
\textit{Thesis:} Modelling of the Multiphase Interactions in a Hydrocyclone using Navier-Stokes and Lattice Boltzmann based Computational Approaches.\\
Supervisor: Prof.\ S.H. Connell (Department of Physics, UJ)\\
Co-supervisor: Prof.\ A.L. Nel (Department of Mechanical Engineering Science, UJ)\\
\href{https://ujcontent.uj.ac.za/esploro/outputs/doctoral/Modelling-of-the-multiphase-interactions-in/9913124607691?institution=27UOJ_INST}{Link to Thesis}

\medskip
\textbf{Master of Engineering (MIng Mechanical Engineering Science) -- \textit{Cum Laude}}\\
\textit{University of Johannesburg} \hfill 2009--2011\\
\textit{Dissertation:} A Computational Fluid Dynamics and Experimental Investigation of an Airflow Window.\\
Supervisor: Prof.\ A. Nurick (Department of Mechanical Engineering Science, UJ)\\
Co-supervisor: Mr.\ D.M. Madyira (Department of Mechanical Engineering Science, UJ)\\
\href{https://ujcontent.uj.ac.za/esploro/outputs/graduate/A-computational-fluid-dynamics-and-experimental/9911487607691?institution=27UOJ_INST}{Link to Dissertation}

\medskip
\textbf{BSc Honours (Applied Mathematics) -- \textit{Cum Laude}}\\
\textit{University of Johannesburg} \hfill 2008--2010
\textit{Minor Dissertation:} The Link between the Finite Element and Finite Difference Methods for the Poisson Equation.\\
Supervisor: Dr. \\ Justin Prentice (Department of Applied Mathematics, UJ)\\

\medskip
\textbf{Bachelor of Engineering (BIng Mechanical Engineering Science)}\\
\textit{University of Johannesburg} \hfill 2004--2008

% ===============================================================
\section{Secondary Education}

\textbf{RAUCALL Secondary School} \hfill 1999--2003\\
Highest Grade Passed: Grade 12 (Matric)\\
Subjects: English (First Language) HG, Afrikaans (Second Language) HG, Mathematics HG, Accounting HG, Physical Science HG, Economics HG.

% ===============================================================
\section{Employment History}

\textbf{Associate Professor} \hfill February 2023 -- Present\\
\textit{University of Pretoria}\\
Line Manager: Prof.\ Schalk Kok\\
Co-ordination and lecturing of the third year Impact of Engineering Activity and Group Work (MIA 320) Module. Supervision of final year mechanical engineering students' research and design projects. Supervision of post-graduate students. Research.

\medskip
\textbf{Staff Research Scientist} \hfill February 2023 -- December 2024\\
\textit{IBM Research -- Africa}\\
Line Managers: Dr.\ Sibusisiwe A. Makhanya and Dr.\ Etienne Vos\\
Conduct Research within the IBM Research Accelerated Discovery Pillar with specific focus on data-driven and machine learning approaches to Climate. Challenge/Project Lead, Patent Ideation, Intern and Student Mentorship.

\medskip
\textbf{Senior Research Associate (Visiting)} \hfill July 2023 -- December 2024\\
\textit{University of Johannesburg}\\
Line Managers: Prof.\ T.C. Jen and Prof.\ Nkosinathi Madushele\\
Conduct Research and Post-graduate supervision.

\medskip
\textbf{Senior Lecturer} \hfill May 2017 -- January 2023\\
\textit{University of Johannesburg}\\
Line Managers: Prof.\ E.T. Akinlabi and Prof.\ T.C. Jen\\
Co-ordination and lecturing of first year Introduction to Engineering Design 1A and 1B modules. Supervision of final year project investigation and design projects. Supervision/co-supervision of Masters and Doctoral students. Departmental co-ordinator for the First Year Seminar. Departmental software and computer labs co-ordinator. Teaching and learning representative on the Departmental Industry Advisory Board (IAB). Research -- Computational Fluid Dynamics (CFD) and engineering education. Former co-ordinator of the Master of Sustainable Energy Programme. Former Departmental short learning programmes (SLPs) co-ordinator.

\medskip
\textbf{Lecturer} \hfill January 2015 -- April 2017\\
\textit{University of Johannesburg}\\
Line Manager: Prof.\ E.T. Akinlabi\\
Co-ordination and lecturing of first year Introduction to Engineering Design 1A and 1B modules. Supervision of final year project investigation and design projects. Co-supervision of Masters students and research.

\medskip
\textbf{Junior Engineer (CFD Analyst)} \hfill 2008--2009\\
\textit{Hatch Africa Pty (Ltd)}\\
Line Manager: Mr.\ S. Ritchie\\
Computational Fluid Dynamics (CFD) modelling for the metals and mineral processing environment. Research of relevant theory, experimental procedures and material properties. Programming of User Defined Functions (C compiler) to improve CFD model accuracy. Technical report writing.

% ===============================================================
\section{Affiliations}

\begin{itemize}
  \item Principal Investigator (PI) in the SA-CERN ATLAS Project -- University of Pretoria ATLAS CERN Institutional Representative/Team Leader.
  \item Registered Professional Engineer (PrEng) with the Engineering Council of South Africa (ECSA).
  \item Full member of the South African Institute of Mechanical Engineering (SAIMechE).
  \item Full member of the South African Association for Theoretical and Applied Mechanics (SAAM).
  \item Vice-President of the SAAM Executive Committee (SAAM ExCo).
  \item Vice-President of the South African National IUTAM (International Union of Theoretical and Applied Mechanics) Committee.
  \item Former Secretary of the SAAM Executive Committee (SAAM ExCo).
  \item Former Secretary of the South African National IUTAM Committee.
  \item Former Full member of the South African Society for Engineering Education (SASEE). Membership concluded in 2023.
\end{itemize}

% ===============================================================
\section{Grants and Other Funding Awarded}

\begin{itemize}
  \item \textbf{2025 -- UP Research Development Programme (RDP)}\\
  \textit{Advancing computational techniques for multiphase flow: Lattice Boltzmann, Deep Learning and Quantum Approaches}\\
  Total Value: R50,000

  \item \textbf{2022 -- UJ URC Research Equipment Grant}\\
  \textit{Preventing COVID-19 with Mathematical Modelling, Digital twins, AI and 4IR Engineered Solutions}\\
  Total Value: R284,517.15

  \item \textbf{2021 -- UJ GES COVID-19 Grant}\\
  \textit{Preventing COVID-19 with Mathematical Modelling, Digital twins, AI and 4IR Engineered Solutions}\\
  Total Value: R80,000

  \item \textbf{2020--2021 -- European Synchrotron Radiation Facility (ESRF)}\\
  \textit{Design and study of equipment for the BEATS beamline at SESAME and other equipment for ESRF beamlines}\\
  Total Value: \texteuro8,750

  \item \textbf{2017--2019 -- NRF Thuthuka Funding Instrument (Post-PhD Track)}\\
  \textit{Modelling of Multiphase Flow in Process Equipment}\\
  Grant Number: TTK160615171464 \quad Total Value: R602,000
\end{itemize}

\subsection*{Principal Investigator -- HPC Projects}

\begin{itemize}
  \item \textit{Multiphase Flow Modelling and Deep Learning}, Project No.\ MECH1739, Centre for High Performance Computing (CHPC). \textit{Active.}
  \item \textit{Modelling of Multiphase Flow in Process Equipment}, Project No.\ MECH0837, CHPC. Concluded 31 January 2023.
  \item \textit{Preventing COVID-19 with Mathematical Modelling, Digital twins, AI and 4IR Engineered Solutions}. Concluded 31 January 2023.
\end{itemize}

% ===============================================================
\section{Formal Collaborations}

\begin{itemize}
  \item \textit{Modelling of Multiphase Flow in Process Equipment} -- Collaborator: Multotec. Period: 2017--2019. Status: Concluded.
  \item \textit{Design and study of the experimental hutch equipment for the BEATS beamline at SESAME} -- Collaborator: ESRF. Period: 2020--2022. Status: Concluded.
  \item \textit{Optimized Heat Transfer for X-Ray Optical Components Designed for High Vibration Stability} -- Collaborator: ESRF. Period: 2019--2023. Status: Involvement Ceased.
\end{itemize}

% ===============================================================
\section{Scholarships Awarded}

\begin{itemize}
  \item January 2012 -- June 2014: Department of Science and Technology (DST) Innovation Scholarship for Doctoral Study.
  \item July 2011 -- June 2014: University of Johannesburg Next Generation Scholarship for Doctoral study.
  \item January--June 2011: NRF Extension Scholarship for Masters studies.
  \item January--March 2011: ENERKEY for Masters Study.
  \item 2009--2010: Department of Science and Technology (DST) Innovation Scholarship for Masters Study.
  \item 2009--2010: University of Johannesburg Next Generation Scholarship for Masters studies.
  \item 2004--2007: Group 5 (Pty) Ltd scholarship for undergraduate studies.
\end{itemize}

% ===============================================================
\section{Postgraduate Supervision}

\subsection*{Masters -- Graduated}
\begin{itemize}
  \item T. Jooma Abbajee, ``Reservoir Computing: A Tool for Predicting Chaotic Dynamical Systems'', 2026, University of Johannesburg \textit{Co-supervisor.}
  \item K.M. Makhanya, ``The Use of Computational Fluid Dynamics for Assessing Flow-Induced Acoustics to Diagnose Lung Conditions'', 2025, University of Johannesburg. \textit{Co-supervisor.}
  \item T.F. Mokoena, ``Design and study of the experimental hutch equipment for the BEATS beamline at SESAME'', University of Johannesburg, 2022. Spent six months at the ESRF. \textit{Main Supervisor.}
  \item T. Ramokoka, ``Modelling Fluid and Particulate Flow Through a Ventriculoperitoneal Shunt in a Variable Temperature Environment'', University of Johannesburg, 2022. \textit{Main (Sole) Supervisor.}
  \item T.B. Molale, ``Numerical Modelling of a Low-Pressure Steam Turbine's Last Stage Rotating Blade'', MEng, University of Johannesburg, 2021. \textit{Co-supervisor.}
  \item A. Potgieter, ``Modelling of a heated gas-solid fluidised bed using Eulerian based models'', MEng, University of Johannesburg, 2020. \textit{Cum Laude. Main Supervisor.}
  \item D.M. Chirnside, ``A Numerical Investigation of Air-Core Formation and Particle Separation in a Hydrocyclone'', MIng, University of Johannesburg, 2019. \textit{Main (sole) supervisor.}
  \item S.A.T. Tina, ``Design Optimization of a Hydrocyclone: Effect of the Cone Shape on the Hydrocyclone Separation Efficiency'', MIng, University of Johannesburg, 2017. \textit{Cum Laude. Co-supervisor.}
  \item M.S.W. Potgieter, ``An Experimental and Computational Fluid Dynamics Investigation of a Counter/Parallel Flow Solar Air Heater'', MIng, University of Johannesburg, 2016. \textit{Cum Laude. Co-supervisor.}
\end{itemize}

\subsection*{Doctoral -- Ongoing}
\begin{itemize}
  \item M. Takoutchouang Saphira Agnes, "An integrated study of fluid–structure interactions in pathological arteries: development of numerical and experimental models for understanding pathophysiological mechanisms and optimizing methods to improve blood flow accuracy", University of Pretoria. \textit{Main supervisor.}
  \item M. Ramokali, "Hybrid classical-quantum computing and machine learning methods for computational fluid dynamics", University of Pretoria. \textit{Main supervisor.}
  \item M.S.W. Potgieter, "Hybrid Lattice Boltzmann - Machine Learning methods for two-phase flow", Univerisity of Pretoria. \textit{Main supervisor.}
  \item A. Essop, "A novel numerical scheme for high speed flows", University of Pretoria. \textit{Main supervisor.} 
  \item T. Jooma Abbajee, ``Graph dynamical Reservoir Computing", University of Johannesburg \textit{Co-supervisor.}
  \item M.P. Connell, ``Search for Higgs boson decays via dark bosons to a four-lepton final state'', University of Johannesburg. \textit{Co-supervisor.}
\end{itemize}

\subsection*{Masters -- Ongoing}
\begin{itemize}
  \item M. Maila, "Modelling of multiphase flow in a hydrocyclone", University of Pretoria. \textit{Main supervisor.}
  \item B. Kazembe, "Modelling of a heated gas-solid fluidised bed using an Eulerian-Eulerian granular model and a Dense Discrete Phase Model (DDPM)", University of Pretoria. \textit{Main supervisor.}
  \item M.Y. Rasool, "Searches for BSM Higgs Decay Channels in the ATLAS Experiment at the Large Hadron Collider", University of Pretoria. \textit{Co-supervisor.} 
\end{itemize}

\subsection*{Masters -- Supervision Ceased}
\begin{itemize}
  \item Confidence Malatjie, ``Computational Fluid Dynamics and Physics Informed Neural Networks'', University of Johannesburg -- Applied Mathematics. \textit{Co-supervisor. Supervision Ceased February 2026.}
\end{itemize}

\subsection*{Doctoral -- Supervision Ceased}
\begin{itemize}
  \item I. Makani, ``Characterization of hydrochar prepared from food waste for the adsorption of H$_2$S from biogas using deep learning, experiment and techno-economic analysis'', University of Pretoria. \textit{Co-supervisor. Supervision Ceased November 2025.}
  \item M.T.L. Lekwana, ``Computational Fluid Dynamics Study of Hemodynamics in the Human Cardiovascular System'', University of Johannesburg. \textit{Main supervisor. Supervision Ceased January 2023.}
  \item A. Potgieter, ``Optimized Heat Transfer for X-Ray Optical Components Designed for High Vibration Stability'', University of Grenoble-Alpes (UGA) / ESRF. \textit{Co-supervisor. Supervision Ceased February 2023.}
\end{itemize}

\subsection*{ATLAS Authorship Qualification Task (AQT) -- Local Supervision}
\begin{itemize}
  \item M.P. Connell, ``Computational Fluid Dynamics Modelling of the N$_2$ Purging Flow Field, Temperature, Humidity and Dew Point Distributions in the Inner Pixels for the ATLAS ITk Upgrade'' -- Completed 1 March 2022. \textit{Local Supervisor.}
  \item P. Mafa Takisa, ``Computational Fluid Dynamics Modelling of the Flow Field, Temperature, Humidity and Dew Point Distributions in the Outer Service Volume (OSV) for the ATLAS ITk Upgrade'' -- Supervision Ceased 31 January 2023. \textit{Local Supervisor.}
\end{itemize}

\subsection*{Mentorship}
\begin{itemize}
  \item Raees Ebrahim Moosa, IBM Research -- Africa Mentorship Programme, BSc Honours Computer Science, University of Witwatersrand. Period: April 2024 -- Present.
  \item R. Seipei, IBM Research Africa -- Intern. Period: April -- October 2023.
  \item Raees Ebrahim Moosa, IBM Research -- Africa Mentorship Programme, BSc Computer Science, University of Witwatersrand. Period: April -- October 2023.
\end{itemize}

% ===============================================================
%%AUTO-GENERATED-PUBLICATIONS%%
\section{Journal and Conference Reviewing}

\begin{itemize}
  \item \textit{Physics of Fluids} -- \href{https://pubs.aip.org/aip/pof}{AIP}
  \item \textit{Energy and Buildings} -- \href{https://www.journals.elsevier.com/energy-and-buildings}{Elsevier}
  \item \textit{SAIMechE R\&D Journal} -- \href{https://www.saimeche.org.za/page/RDJournal}{Link}
  \item \textit{Environmental Science and Pollution Research} -- \href{https://www.springer.com/journal/11356}{Springer}
  \item \textit{SAIEE Africa Research Journal} (special issue)
  \item \textit{JOM -- Journal of The Minerals, Metals \& Materials Society (TMS)} (special issue)
  \item \textit{Applied Energy} -- \href{https://www.journals.elsevier.com/applied-energy}{Elsevier}
  \item \textit{Building and Simulation} -- \href{https://www.springer.com/journal/12273}{Springer}
  \item Reviewer: \textit{SAIP 2025} (69th Annual Conference); \textit{SACAM 2025} (14th Conference)
  \item Reviewer: \textit{ICLR 2024} -- Three workshop proposals reviewed.
  \item Reviewer: \textit{SAIP 2024} (68th Annual Conference)
  \item Reviewer: \textit{WEEF/IFEES/GEDC 2022}, Cape Town (two abstracts)
  \item Reviewer: \textit{SAIP 2022} (66th Annual Conference)
  \item Reviewer: \textit{WEEF/GEDC 2021}, Madrid, Spain (two papers)
  \item Abstract reviewer: \textit{2nd Biennial SOTL in the South Conference}, Bloemfontein, October 2019
  \item Reviewer: \textit{SMPM 2019}, North West, 8--10 March 2019
  \item Reviewer: \textit{SACAM 2018}, Vanderbijlpark, 17--19 September 2018
  \item Reviewer: \textit{SACAM 2012}, Johannesburg, 3--5 September 2012
\end{itemize}

% ===============================================================
\section{Member of Conference Organising Committees}

\begin{itemize}
  \item Member of the Local Organising Committee for the \textit{ 7th Biennial “Workshop on Discovery Physics at the LHC” (Kruger2026) Conference} -- Hosted by SA-CERN.
  \item Member of the Local Organising and Scientific Committee for the \textit{2025 SAIMechE Central Branch Conference on Mechanical Engineering and Related Disciplines} -- Hosted by Wits University.
  \item Member of the Local Organising Committee for \textit{SMPM 2019}, North West, 8--10 March 2019 -- Hosted by UJ.
  \item Member of the Local Organising Committee for \textit{SACAM 2012}, Johannesburg, 3--5 September 2012 -- Hosted at UJ.
\end{itemize}

% ===============================================================
\section{References}

\begin{tabular}{@{}lll@{}}
\textbf{Dr.\ Sibusisiwe A. Makhanya} & Senior Research Manager, IBM Research SA & \href{mailto:Sibusisiwe.Makhanya@ibm.com}{Sibusisiwe.Makhanya@ibm.com} \\[4pt]
\textbf{Dr.\ Thomas Brunchwiler} & Principal Research Scientist, IBM Research & \href{mailto:tbr@zurich.ibm.com}{tbr@zurich.ibm.com} \\[4pt]
\textbf{Prof.\ Nkosinathi Madushele} & Head of Department, UJ Mechanical Eng. & \href{mailto:nmadushele@uj.ac.za}{nmadushele@uj.ac.za} \\
& +27 11 559 2538 / +27 78 841 9095 & \\[4pt]
\textbf{Prof.\ Simon H. Connell} & Professor, UJ Mechanical Eng. & \href{mailto:shconnell@uj.ac.za}{shconnell@uj.ac.za} \\
& +27 11 559 4380 / +27 82 945 7508 & \\[4pt]
\textbf{Prof.\ Zachary S. Simpson} & Assoc.\ Professor, Engineering Education, UJ & \href{mailto:zsimpson@uj.ac.za}{zsimpson@uj.ac.za} \\
& +27 11 559 3683 / +27 84 775 9427 & \\[4pt]
\textbf{Dr.\ Tamara R. Govindasamy} & Research Scientist, IBM Research Africa & \href{mailto:Tamara.Govindasamy@ibm.com}{Tamara.Govindasamy@ibm.com} \\
\end{tabular}

\end{document}
